A pipeline to analyse time-course gene expression data

### 2020-07-17 scripts/manuscript.Rmd
switch from DataFrame to matrix

```{r genesVsCentroids, fig.height=6, fig.width=6}
cluster_of_interest = 2
cluster2Genes = names(
    kmeans_clusters$clusters[kmeans_clusters$clusters==cluster_of_interest])
dataToPlot=rbind(as.matrix(assay(de_moanin_model[cluster2Genes[3:6],])), 
    "Centroid"=kmeans_clusters$centroids[cluster_of_interest,])
plot_splines_data(de_moanin_model,  data=dataToPlot, 
    colors=ann_colors$Group, smooth=TRUE,simpleY =FALSE,
    mar=c(1.5,2.5,2,0.1))
```

>>>>

```{r genesVsCentroids, fig.height=6, fig.width=6}
cluster_of_interest = 2
cluster2Genes = names(
    kmeans_clusters$clusters[kmeans_clusters$clusters==cluster_of_interest])
dataToPlot=rbind(assay(de_moanin_model[cluster2Genes[3:6],]), 
    "Centroid"=kmeans_clusters$centroids[cluster_of_interest,])
plot_splines_data(de_moanin_model,  data=dataToPlot, 
    colors=ann_colors$Group, smooth=TRUE,simpleY =FALSE,
    mar=c(1.5,2.5,2,0.1))
```
